Component-based Software Development Framework \\for Embedded IoT Devices（仮）

### 2017-11-09 ipsj/paper.tex
Update

\usepackage[dvipdfmx]{graphicx}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{float}
\usepackage{enumerate,cite,url}
\usepackage{listings,jlisting}
\lstset{%
    language={c},%
    basicstyle={\small},%
    identifierstyle={\small},%
    commentstyle={\footnotesize\itshape},%
    keywordstyle={\small},%\bfseries},%
    ndkeywordstyle={\small},%
    stringstyle={\small\it},
    frame={tb},
    breaklines=true,
    columns=[l]{fullflexible},%
    numbers=left,%
    xrightmargin=0zw,%
    xleftmargin=3zw,%
    numberstyle={\scriptsize},%
    stepnumber=1,
    numbersep=1zw,%
    lineskip=-0.5ex%
}

@@

This section describes the system model of the proposed framework, including basic technologies such as TECS.
The system model of the proposed framework is shown in Fig.\ref{fig:SystemModel}.

The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}\cite{par:mrubyonTECS2}, and utilizes two technologies: mruby and TECS.
In this section, TECS,  mruby, and mruby on TECS framework are described.

@@

In this paper, TOPPERS/ASP3 \cite{par:ASP}, \cite{url:ASP} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} .
However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs}.

@@

The mruby-TECS bridge generates a {\it celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.

The generated mruby-TECS bridge supports registration of classes and methods for mruby.
Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.

@@

@@

Fig.\ref{src:TLSFBuild} shows the build description of the TLSF memory allocator component shown in Fig.\ref{fig:WithTECS}\footnote{Other call/entry ports, attributes, and valuables are actually described, but it is omitted here for the simplicity.}.
Two sets of task components and TLSF components are combined.
Each memory pool size can be configured as an variable (Lines 5 and 11 in Fig.\ref{src:TLSFBuild}).
Fig.\ref{src:TLSFC} is the part of the code actually calling the function of the TLSF memory allocator component.
The use part shows a function that the mruby VM allocates memory in the mruby on TECS framework\cite{par:mrubyonTECS}\cite{par:mrubyonTECS2} which is introduced in Section \ref{sec:mrubyonTECS}.
Lines 8 calls the {\it free} function of the TLSF memory allocator component.
{\it cMalloc\_} represents the name of the calle port (Lines 2 in Fig.\ref{src:TLSFBuild}).
Likewise, Lines 13 and 17 call the function for memory allocation.
The heap area of {\it TLSFMalloc\_001} component is used if the code of \ref{src:TLSFC} is executed in {\it Task\_001}, and if that is executed in {\it Task\_002}, the heap area of {\it TLSFMalloc\_002} component is used, respectively.
In this way, in the component-based development using TECS, it is possible to operate with the same code without modifying the C code, although the cells are different.

>>>>

\usepackage[dvipdfmx]{graphicx}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{float}
\usepackage{enumerate,cite,url}
\usepackage{color}
\usepackage{listings,jlisting}
\lstset{%
    language={c},%
    basicstyle={\small},%
    identifierstyle={\small},%
    commentstyle={\footnotesize\itshape},%
    keywordstyle={\small},%\bfseries},%
    ndkeywordstyle={\small},%
    stringstyle={\small\it},
    frame={tb},
    breaklines=true,
    columns=[l]{fullflexible},%
    numbers=left,%
    xrightmargin=0zw,%
    xleftmargin=3zw,%
    numberstyle={\scriptsize},%
    stepnumber=1,
    numbersep=1zw,%
    lineskip=-0.5ex%
}

@@

This section describes the system model of the proposed framework, including basic technologies such as TECS and mruby.
The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}\cite{par:mrubyonTECS2}, and utilizes two technologies: mruby and TECS.
The system model of the proposed framework is shown in Fig.\ref{fig:SystemModel}.
In the proposed framework, each mruby program runs on a RiteVM mapped to a componentized task of an RTOS.
mruby programs can call the TINET functions required for network programming through the mruby-TECS bridge, and thus software to be embedded in IoT devices can be developed.
Moreover, the proposed framework comprises TLSF+TECS.
TLSF+TECS is utilized for memory management of mruby's RiteVMs and TINET+TECS, which helps to improve the efficiency of memory consumption.

The following subsection explains TECS, mruby, and mruby on TECS framework.

@@

In this paper, TOPPERS/ASP3 \cite{par:ASP}, \cite{url:ASP} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} .
However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/ASP3 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs}.

@@

The mruby-TECS bridge generates a {\it celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.
The generated mruby-TECS bridge supports registration of classes and methods for mruby.
Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.

@@

\textcolor{red}{TODO: セクションの概要を追加}

\subsection{Extended mruby on TECS (仮)}

\textcolor{red}{TODO: mrubyからTINETを利用する説明とかmrubyでエコーサーバのコード例とか}

@@

Fig.\ref{src:TLSFBuild} shows the build description of the TLSF memory allocator component shown in Fig.\ref{fig:WithTECS}\footnote{Other call/entry ports, attributes, and valuables are actually described, but it is omitted here for the simplicity.}.
Two sets of task components and TLSF components are combined.
Each memory pool size can be configured as an variable (Lines 5 and 11 in Fig.\ref{src:TLSFBuild}).
Fig.\ref{src:TLSFC} is the part of the code actually calling the function of the TLSF memory allocator component.
The use part shows a function that the mruby VM allocates memory in the mruby on TECS framework\cite{par:mrubyonTECS}\cite{par:mrubyonTECS2} which is introduced in Section \ref{sec:mrubyonTECS}.
Lines 8 calls the {\it free} function of the TLSF memory allocator component.
{\it cMalloc\_} represents the name of the call port (Lines 2 in Fig.\ref{src:TLSFBuild}).
Likewise, Lines 13 and 17 call the function for memory allocation.
The heap area of {\it TLSFMalloc\_001} component is used if the code of \ref{src:TLSFC} is executed in {\it Task\_001}, and if that is executed in {\it Task\_002}, the heap area of {\it TLSFMalloc\_002} component is used, respectively.
In this way, in the component-based development using TECS, it is possible to operate with the same code without modifying the C code, although the cells are different.
